A Unified Treatment of Tractability for \\ Approximation Problems Defined on Hilbert Spaces

### 2024-04-21 Older_versions/Generalized_Tractability_Submission_2.tex
Updates from Overleaf

\input{FJHDef.tex}
% Modify the elsarticle-num-names bibliography style to sort references alphabetically
\makeatletter
\renewcommand\@biblabel[1]{#1.}
\makeatother

@@

@@

We define $\ch_{\kor,d,\bsa,\bsb}$ as the space of all one-periodic functions $f$ with absolutely convergent Fourier series given by $f(\bsx) = \sum_{\bsh \in \ZZ^d} \widehat{f}(\bsh) \exp(2 \pi \sqrt{-1}\bsh'\bsx)$, 
and with finite norm 
$||f||_{\kor,d,\bsa,\bsb}:=\langle f, f\rangle_{\kor,d,\bsa,\bsb}^{1/2}$,
where the inner product is given by
\[
 \langle f, g\rangle_{\kor,d,\bsa,\bsb}:=
 \sum_{\bsh\in\ZZ^d} r_{d,\bsa,\bsb} (\bsh) 
 \widehat{f} (\bsh) \overline{\widehat{g}(\bsh)}.
\]
%where $\widehat{f}$ and $\widehat{g}$ denote the Fourier coefficients of $f$ and $g$, respectively.
Let us consider $L_2$-approximation, i.e., $\SOL_d:\ch_{\kor,d,\bsa,\bsb}\to L_2([0,1]^d)$, $\SOL_d(f)=f$, and let us allow arbitrary continuous linear functionals as information. One can show that the singular values  for this choice of $\SOL_d$ are given by
\begin{equation}\label{eq:eigenvalues}
 \left\{\lambda_{n,d}\colon n\in\NN\right\}=\left\{\left(r_{d,\bsa,\bsb} (\bsh)\right)^{-1/2}\colon \bsh\in\ZZ^d\right\}
 =\left\{\omega^{\frac{1}{2}\sum_{j=1}^{d}a_j \abs{h_j}^{b_j}}\colon \bsh\in\ZZ^d\right\}.
\end{equation}

@@

\bibliography{FJHOwn23,FJH23,Further_references}
%\bibliographystyle{elsarticle-num}
\bibliographystyle{plain}
%\bibliographystyle{elsarticle-harv}
%\bibliographystyle{elsarticle-num-names}

\end{document}

>>>>

\input{FJHDef.tex}

@@

\bibliography{FJHOwn23,FJH23,Further_references}
\bibliographystyle{elsarticle-num}

@@

We define $\ch_{\kor,d,\bsa,\bsb}$ as the space of all one-periodic functions $f$ with absolutely convergent Fourier series given by $f(\bsx) = \sum_{\bsh \in \ZZ^d} \widehat{f}(\bsh) \exp(2 \pi \sqrt{-1}\bsh'\bsx)$, 
and with finite norm 
$||f||_{\kor,d,\bsa,\bsb}:=\langle f, f\rangle_{\kor,d,\bsa,\bsb}^{1/2}$,
where the inner product is given by
\[
 \langle f, g\rangle_{\kor,d,\bsa,\bsb}:=
 \sum_{\bsh\in\ZZ^d} r_{d,\bsa,\bsb} (\bsh) 
 \widehat{f} (\bsh) \overline{\widehat{g}(\bsh)}.
\]
%where $\widehat{f}$ and $\widehat{g}$ denote the Fourier coefficients of $f$ and $g$, respectively.
Let us consider $L_2$-approximation, i.e., $\SOL_d:\ch_{\kor,d,\bsa,\bsb}\to L_2([0,1]^d)$, $\SOL_d(f)=f$, and let us assume
$\Lambda^{\rm all}$ as the information class. One can show that the singular values  for this choice of $\SOL_d$ are given by
\begin{equation}\label{eq:eigenvalues}
 \left\{\lambda_{n,d}\colon n\in\NN\right\}=\left\{\left(r_{d,\bsa,\bsb} (\bsh)\right)^{-1/2}\colon \bsh\in\ZZ^d\right\}
 =\left\{\omega^{\frac{1}{2}\sum_{j=1}^{d}a_j \abs{h_j}^{b_j}}\colon \bsh\in\ZZ^d\right\}.
\end{equation}

@@

\end{document}
z
